---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
require(plyr)
require(ggplot2)
unzip("activity.zip")
activity <- read.csv("activity.csv", header = TRUE)
activity <- transform(activity, date = as.Date(date))
```

## What is mean total number of steps taken per day?

Find the total number of steps taken per day.
```{r}
stepsPerDay <- tapply(activity$steps, activity$date, sum, na.rm=TRUE)
```

Plot a histogram of the total number of steps taken per day.
```{r}
qplot(stepsPerDay, xlab='Total steps per day', ylab='Frequency using binwith 800', binwidth=800)
```

Compute the `mean` and `median` total number of steps taken per day.
```{r}
meanStepsPerDay <- mean(stepsPerDay)
medianStepsPerDay <- median(stepsPerDay)
```

- The mean is `r format(meanStepsPerDay)`
- The median is `r format(medianStepsPerDay)`

## What is the average daily activity pattern?
```{r}
interval <- aggregate(activity[1],by=activity[3],FUN=mean,na.rm=TRUE)
plot(x=interval$interval, y=interval$steps,main="Average Steps",type="l",
     xlab="Interval", ylab="No. of Steps")
```

**Maximum Steps**

```{r}
max_interval <- interval[interval$steps==max(interval$steps),]

max_interval[1] # maximum interval
round(max_interval[2],1) # maximum steps per interval
```

The maximum average steps per period occur at interval `r max_interval[1]`, with an average of `r round(max_interval[2],1)` steps per 5 minutes.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
